Laziness in R

### 2019-02-01 report/report.Rmd
Add report step to create report from summarized and visualized data

---
title: "Laziness in R"
output:
  html_document:
    toc: true
    theme: united
params:
  output_directory: ../latest
  image_format: png
editor_options:
  chunk_output_type: console
---

@@

```{r paths, echo = FALSE}

function_definitions_dirpath <- path(params$output_directory, "function-definitions")
parameter_usage_dirpath <- path(params$output_directory, "parameters")
visualizations <- path(parameter_usage_dirpath, "visualizations")
summary <- path(parameter_usage_dirpath, "summary")
```

```{r datatsets, echo = FALSE}
import_data_table <- function(name) {
    promisedyntracer::read_data_table(path(summary, name))
}

@@

show_graph <- function(graphname) {
    include_graphics(path(visualizations, graphname))
}

show_graphs <- function(first_graphname, second_graphname) {
    load_graph <- function(graphname) {
        grid::rasterGrob(as.raster(readPNG(path(visualizations, graphname))),
                         interpolate = TRUE)
    }
    grid.arrange(load_graph(first_graphname),
                 load_graph(second_graphname),
                 ncol = 2)
}

>>>>

---
title: "Laziness in R"
output:
  html_document:
    toc: true
    theme: united
params:
  summarized_data_dirpath: ../latest/analysis/summarized
  visualized_data_dirpath: ../latest/analysis/visualized
  image_format: png
editor_options:
  chunk_output_type: console
---

@@

```{r datatsets, echo = FALSE}
import_data_table <- function(name) {
    promisedyntracer::read_data_table(path(params$summarized_data_dirpath, name))
}

@@

show_graph <- function(graphname) {
    include_graphics(path(params$visualized_data_dirpath, graphname))
}

show_graphs <- function(first_graphname, second_graphname) {
    load_graph <- function(graphname) {
        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
                                                graphname))),
                         interpolate = TRUE)
    }
    grid.arrange(load_graph(first_graphname),
                 load_graph(second_graphname),
                 ncol = 2)
}
